% !TEX program = xelatex

\documentclass{resume}

%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Xingguo\  Jia}

\basicInfo{
  \email{jiaxg1998@sjtu.edu.cn} \textperiodcentered \
  \phone{(+86) 132-6262-6313} \textperiodcentered\ 
  \faGithub\ {https://github.com/snake0}}
  % \phone{(+86) 131-221-87xxx} \textperiodcentered\ 
  % \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2020 -- Present}
\textit{Graduate student} in Software Engineering (SE), expected March 2023, \textbf{GPA:} 3.83/4.00
\begin{itemize}
  \item Trusted Cloud Group (TCloud) \textbf{Advisor:} Prof. Zhengwei Qi
  \item \textbf{Research Interests:} Operating System, distributed system, virtualization
\end{itemize}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2016 -- 2020}
\textit{B.E.} in Software Engineering (SE), \textbf{GPA:} 3.50/4.30

\section{\faUsers\ Research Experiences}
\datedsubsection{\textbf{SJTU, TCloud}, Shanghai, China}{Jun. 2019 -- Present}
\textbf{\textit{GiantVM:}} Top-down performance evaluation and optimizations using a scheduling algorithm.

\datedsubsection{\textbf{Huawei Co. Hangzhou Research Inst.}, as an intern, Hangzhou, China}{Feb. 2022 -- Aug. 2022}
\textbf{\textit{Memory Pool:}} Memory pool design and implementation based on recent high-speed networks.

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faInfo\ Projects}
\datedsubsection{\textbf{DaS:} DSM-aware Scheduler for GiantVM\ \ \href{https://github.com/GiantVM/Linux-DSM/tree/taco-eval}{\faGithubSquare}}{Aug. 2020 -- Oct. 2021} 

On GiantVM, memory-intensive applications could suffer from cross-node page sharing, leading to performance collapse. To overcome the bottleneck, we design DSM-aware Scheduler (DaS) in the guest kernel. When benchmarking with NPB, DaS achieves a performance boost of up to 3.5$\times$, compared to CFS. 

\datedsubsection{\textbf{LaS:} Load-aware Scheduler based on GiantVM\ \ \href{https://github.com/snake0/bachelor-thesis}{\faGithubSquare}}{Apr. 2020 -- Aug. 2020}

Thanks to the SSI abstraction of GiantVM, workload migration could be done simply by guest-level
scheduling. Also, DSM allows standby pages in the migration destination, which need not be transferred through
the network. The saved network bandwidth is 68\% on average, compared to VM live migration.

\datedsubsection{{\textbf{kRDMA:} RDMA-based network operation APIs}\ \ \href{https://github.com/snake0/krdma}{\faGithubSquare}}{Apr. 2022 -- Jun. 2022}
The IB verbs interface is hard to use for kernel-level programming, and may suffer from inefficiencies if not used in a proper way. We introduce kRDMA, a set of kernel-level APIs for RDMA-based network operations, which simplifies the way to use RDMA. To boost performance, we register physical addresses with RDMA NICs to reduce cache consumption.

\section{\faGraduationCap\ Publications}
\begin{itemize}
\item Jin Zhang, Zhuocheng Ding, Yubin Chen, \textbf{Xingguo Jia}, Boshi Yu, Zhengwei Qi, and Haibing Guan. 2020. GiantVM: a Type-II Hypervisor Implementing Many-to-one Virtualization. In \textbf{VEE'20}
\item \textbf{Xingguo Jia$^*$}, Jin Zhang$^*$, Boshi Yu, Xingyue Qian, Zhengwei Qi, and Haibing Guan. 2022. GiantVM: A Novel Distributed Hypervisor for Resource Aggregation with DSM-aware Optimizations. In \textbf{TACO'22}
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages}: C > C++ > Python > Shell \textbf{Tools}: \LaTeX, Git, GDB \textbf{Systems}: Linux, QEMU
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{First-class} academic scholarship, \textbf{SJTU} }{Dec. 2021}
%\datedline{Successful Participant, \textbf{MCM} }{Jan. 2019}
\datedline{"System Virtualization: Principles and Practices", Outstanding Contribution Award, \textbf{MOE of PRC}}{Jan. 2022}

%\section{\faUsers\ Teaching Experiences}
%\datedline{Advanced Data Structure (SE2322), \textit{teaching assistant}, \textbf{SJTU} }{Apr. 2021 -- Jul. 2021}
%\datedline{Advanced Cloud OS (EI6709), \textit{teaching assistant}, \textbf{SJTU} }{Nov. 2021 -- Dec. 2021}

%\section{\faUsers\ Teaching Experiences}
%\datedline{Advanced Cloud Operating Systems, SJTU }{Dec. 2021}
%\datedline{Advanced Data Structure, SJTU }{Jun. 2021}

%\section{\faInfo\ Miscellaneous}
%\begin{itemize}[parsep=0.5ex]
%  \item GiantVM: https://giantvm.github.io/
%%  \item GitHub: https://github.com/snake0
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}

